%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}
% \usepackage{natbib}


\name{Wah Loon Keng} % Your name

\address{Box 7277, Lafayette College, 111 Quad Drive, Easton, PA 18042 } % Your address
\address{\tt{
\hfill (484) 541-5913 
\hfill \href{mailto:kengw@lafayette.edu}{kengw@lafayette.edu} 
\hfill \href{https://github.com/kengz}{https://github.com/kengz} \hfill}} % Your phone number and email

\begin{document}

\begin{rSection}{Cover Letter}


\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

Wah Loon Keng,\\
Box 7277, Lafayette College,\\
111 Quad Drive,\\
Easton, PA 18042.\\

July $16^{th}$ 2015\\


Hello,

I am Keng, an undergraduate who loves theories $-$ Mathematics, Computer Science and Physics. What I love more is to put the knowledge to good use $-$ please hear my confession:

Being a theorist, I feel the need for redemption, to contribute back by solving real world problems. I spent the last three summers thinking and writing theories, mainly on computational geometry and foundations of quantum mechanics. Don't get me wrong, I loved my work; at Perimeter Institute, they gave me an office, fed me cookies, and even let me scribble all over their wall to discuss really crazy ideas - we were rewriting the foundations of quantum mechanics using quantum computation and paradoxes.

When I stepped back to see the Great Wall of Sribbles with my fellow theorists, I realized some of these ideas would grow into new theories that reshape the world. It was a moment of clarity $-$ I knew my purpose, what got me excited $-$ I wanted to contribute.

$``$If we theorists could too tackle problems that are more relevant and urgent, imagine the implications,$"$ I asked myself. This is why I turn to Computer Science; abstract math is cool, but it'd be even cooler if I can build something that impacts the world - I want to build things using my knowledge.

Currently I still wish to go into graduate school for machine learning and AI, because the ultimate thing I wish to build is an intelligent machine. Meanwhile, I'd like an adventure in the industry, and I love to code and build - I love to see my thoughts come true.

If you have a position for someone who loves to tinker and build thing, I'm up for it. Be it algorithms, statistics, vector spaces, machine learning, or rapid deployment of an app on a server, I'll think, theorize, design and build from start to end.

Lastly, I appreciate your attention.\\


Regards,\\
{\em Keng}





%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

% \bibliographystyle{plain}
% name without .bib:
% \bibliography{research}

\end{document}


